% !TeX program = pdflatex

\RequirePackage[l2tabu,orthodox]{nag}
\documentclass[11pt,letterpaper]{report}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{ebgaramond}
\usepackage{tgheros}

\usepackage[USenglish]{babel}
\usepackage[strict,autostyle]{csquotes}
\usepackage[babel=true]{microtype}

\usepackage{datetime}
\usepackage{enumitem}
\usepackage{geometry}
\usepackage{setspace}
\usepackage{tabto}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{xcolor}

\newcommand{\myname}{Hassan R. S. Andrabi}
\newcommand{\listtabwidth}{1.9cm}
\newcommand{\namefont}[1]{{\normalfont\bfseries\Huge{#1}}}
\definecolor{cvred}{HTML}{850900}

\SetTracking{encoding=*, family=\sfdefault}{30}
\titleformat{\section}{\color{cvred}\lsstyle\sffamily\small\bfseries\uppercase}{}{}{}{}
\titlespacing{\section}{0pt}{30pt plus 4pt minus 4pt}{8pt plus 2pt minus 2pt}

\titleformat{\subsection}{\lsstyle\sffamily\footnotesize\bfseries}{}{}{}{}
\titlespacing{\subsection}{0pt}{16pt plus 4pt minus 4pt}{4pt plus 2pt minus 2pt}

\geometry{body={6.5in, 9.0in},
    left=1.0in,
    top=1.0in}

\setlength\parindent{0em}
\setstretch{0.9}
\newcommand{\listitemspace}{0.25em}

\renewenvironment{itemize}
{\begin{list}{}{\setlength{\leftmargin}{0em}
                \setlength{\parskip}{0em}
                \setlength{\itemsep}{\listitemspace}
                \setlength{\parsep}{\listitemspace}}}
{\end{list}}

\TabPositions{\listtabwidth}
\newlist{tablist}{description}{3}
\setlist[tablist]{leftmargin=\listtabwidth,
    labelindent=0em,
    topsep=0em,
    partopsep=0em,
    itemsep=\listitemspace,
    parsep=\listitemspace,
    font=\normalfont}

\newdateformat{monthyeardate}{\monthname[\THEMONTH] \THEYEAR}

\hypersetup{
    colorlinks  = true,
    urlcolor    = black,
    citecolor   = black,
    linkcolor   = black,
    pdfauthor   = {\myname},
    pdftitle    = {\myname: Curriculum Vitae},
    pdfsubject  = {Curriculum Vitae},
    pdfpagemode = UseNone
}

\begin{document}
    \raggedright{}

    \namefont{\myname}

    \vspace{1em}
    \begin{minipage}[t]{0.700\textwidth}
        Centre for Brain, Mind, \& Markets \\
        Department of Finance \\
        University of Melbourne
    \end{minipage}
    \begin{minipage}[t]{0.295\textwidth}
        \raggedleft{}
        \href{mailto:hassan.andrabi@unimelb.edu.au}{hassan.andrabi@unimelb.edu.au} \\
        +61 431 452 426 \\
        \href{https://hassan.andra.bi}{hassan.andra.bi}
    \end{minipage}

    \section*{Education}

    \begin{tablist}
        \item[PhD] \tab{}Decision, Risk, and Financial Sciences, University of Melbourne, 2027
        \item[MCom] \tab{}Decision, Risk, and Financial Sciences, University of Melbourne, 2024
        \item[Hons] \tab{}Finance, University of Melbourne, 2020
        \item[BCom] \tab{}Commerce, University of Melbourne, 2019
    \end{tablist}

    \section*{Research Areas}

    \begin{itemize}
        \item Markets: information aggregation, market design, and the role of incentives.
        \item Computational complexity theory: combinatorial problems, phase transitions, and human problem-solving.
        \item Simulation modelling to evaluate the health and economic impacts of public health interventions.
    \end{itemize}

    \section*{Publications}

    \subsection*{Journal Articles}

    \begin{tablist}
        \item[2025] \tab{}S. Bode, A. Varsamis, Z. A. Xu, M. Jiwa, H. Andrabi, N. Egorova-Brumley, C. Morawetz.\ \enquote{When We Want to Know the Bad News: Exploring Information-Seeking for Unavoidable Pain Stimuli.} \textit{Cognition and Emotion}.\ \href{https://doi.org/10.1080/02699931.2025.2597887}{doi.org/10.1080/02699931.2025.2597887}
        \item[2024] \tab{}D. Ait Ouakrim, T. Wilson, A. Waa, R. Maddox, H. Andrabi, S. R. Mishra, J. A. Summers, C. E. Gartner, R. Lovett, R. Edwards, N. Wilson, T. Blakely.\ \enquote{Tobacco Endgame Intervention Impacts on Health Gains and Maori: Non-Maori Health Inequity: A Simulation Study of the Aotearoa/New Zealand Tobacco Action Plan.} \textit{Tobacco Control} 2 (33), 173-184. \href{https://doi.org/10.1136/tc-2022-057655}{doi.org/10.1136/tc-2022-057655}
        \item[2023] \tab{}S. R. Mishra, T. Wilson, H. Andrabi, D. Ait Ouakrim, A. Li, E. Akpan, R. Bentley, T. Blakely.\ \enquote{The Total Health Gains and Cost Savings of Eradicating Cold Housing in Australia.} \textit{Social Science \& Medicine} 334 (115954).\ \href{https://doi.org/10.1016/j.socscimed.2023.115954}{doi.org/10.1016/j.socscimed.2023.115954}
        \item[2023] \tab{}J. Szanyi, T. Wilson, S. Howe, J. Zeng, H. Andrabi, S. Rossiter, T. Blakely.\ \enquote{Epidemiologic and Economic Modelling of Optimal COVID-19 Policy: Public Health and Social Measures, Masks and Vaccines in Victoria, Australia.} \textit{The Lancet Regional Health -- Western Pacific} 32 (100675).\ \href{https://doi.org/10.1016/j.lanwpc.2022.100675}{doi.org/10.1016/j.lanwpc.2022.100675}
    \end{tablist}

    \section*{Invited Talks}

    \subsection*{Seminars and Workshops}
    \begin{tablist}
        \item[2026] \tab{}\enquote{Incentives for Discovery in Computationally Hard Environments.} Workshop on Computational Complexity and Economic Decision Making. University of Cambridge. Cambridge, UK. May 27.
        \item[2026] \tab{}\enquote{The Impact of Price Signals on Effort and Productivity in a `Hard' Task.} Workshop on Dynamic Decision Making: Minds, Models, and Markets. The University of Sydney. Sydney, Australia. Apr 14.
        \item[2025] \tab{}\enquote{Phase Transition in the 0-1 Knapsack Problem.} Leverhulme International Professorship in Neuroeconomics Complexity Seminar. University of Cambridge. Cambridge, UK. Mar 3.
        \item[2024] \tab{}\enquote{Prices as Information Signals.} Leverhulme International Professorship in Neuroeconomics Complexity Seminar. University of Cambridge. Cambridge, UK. Nov 19.
    \end{tablist}

    \subsection*{Conference Activity\footnote{Presenting author \textit{italicised} if other than first author.}}
    \begin{tablist}
        \item[2026] \tab{}H. Andrabi, P. Bossaerts, N. Yadav.\ \enquote{Incentives for Discovery in Computationally Hard Environments.} International Association for Research in Economic Psychology, Motives and Preferences in Economic Decisions. Castellón, Spain. Jun 9.
        \item[2026] \tab{}H. Andrabi, P. Bossaerts, N. Yadav.\ \enquote{Incentives for Discovery in Computationally Hard Environments.} Asia-Pacific Meeting of the Economic Science Association. Melbourne, Australia. Apr 9.
        \item[2026] \tab{}H. Andrabi, P. Bossaerts, N. Yadav.\ \enquote{The Invisible Hand: How Markets Guide Effort and Productivity} Experimental Finance Asia/Pacific. Melbourne, Australia. Apr 8.
        \item[2026] \tab{}H. Andrabi, P. Bossaerts, N. Yadav.\ \enquote{The Impact of Price Signals on Effort and Productivity in a `Hard' Task.} Australasian Mathematical Psychology Conference. Singapore. Feb 27.
        \item[2025] \tab{}H. Andrabi, P. Bossaerts, \textit{K. Ioannidis}, R. Woods, N. Yadav.\ \enquote{Markets or Patents? Experiments on Collective Innovation and Information Aggregation} Society for Experimental Finance Conference. Maastricht, Netherlands. Jun 12.
        \item[2024] \tab{}H. Andrabi, P. Bossaerts, \textit{K. Ioannidis}, R. Woods, N. Yadav.\ \enquote{Markets spread knowledge to overcome computational complexity.} Society for Experimental Finance Conference. Stavanger, Norway. Jun 25.
        \item[2024] \tab{}H. Andrabi, P. Bossaerts, K. Ioannidis, R. Woods, N. Yadav.\ \enquote{Markets Reveal Optimal Solutions to Complex Problems.} Society for Neuroeconomics Conference. Cascais, Portugal. Oct 11.
    \end{tablist}

    \section*{Grants and Awards}

    \subsection*{Awards and Honors}

    \begin{tablist}
        \item[2025] \tab{}Vernon Smith Young Talent Award, Society for Experimental Finance. \$4,000 USD.
        \item[2024] \tab{}Melbourne Global Scholars Award for High Achieving Students, Faculty of Business and Economics, University of Melbourne. \$1,500 AUD.
        \item[2023] \tab{}Best Research Paper by Discipline Award (Methodology), School of Population and Global Health, University of Melbourne. \$1,500 AUD.
        \item[2022] \tab{}MPSGH Research Achievement Award, School of Population and Global Health, University of Melbourne. \$1,500 AUD.
    \end{tablist}

    \subsection*{Competitive Scholarships}
    \begin{tablist}
        \item[2024] \tab{}International Study Scholarship, Faculty of Business and Economics, University of Melbourne. \$5,000 AUD.
        \item[2023] \tab{}Doctoral Program Scholarship, Faculty of Business and Economics, University of Melbourne. \$37,000 AUD p.a.
        \item[2014] \tab{}Kwong Lee Dow Scholarship for High Achieving Students, University of Melbourne. \$2,500 AUD.
    \end{tablist}

    \section*{Teaching}


    \begin{tablist}
        \item[2026] \tab{}Behavioural Finance (undergraduate), TA; Principles of Finance (undergraduate), TA
        \item[2025] \tab{}Machine Learning in Finance (postgraduate), head TA; Principles of Finance (undergraduate), TA
        \item[2024] \tab{}Machine Learning in Finance (postgraduate), head TA; Algorithmic Trading (postgraduate), TA; Capstone Studies in Finance (postgraduate), TA
        \item[2023] \tab{}Machine Learning in Finance (postgraduate), TA
        \item[2021] \tab{}Contemporary Epidemiology Short Course (postgraduate), Instructor
    \end{tablist}

    \section*{Professional Employment}

    \begin{tablist}
        \item[2025--] \tab{}Software Engineer (frontend), Centre for Brain, Mind, \& Markets, University of Melbourne
        \item[2020--23] \tab{}Software Engineer (Simulation Modelling), Population Interventions Unit, University of Melbourne
        \item[2019--20] \tab{}Accounting and Advisory, MJC Partners
    \end{tablist}

    \section*{Service}

    \subsection*{Service to the Field}
    \begin{tablist}
        \item[2025] \tab{}PyKP, a Python package for the 0-1 Knapsack Problem.\ \url{https://pykp.readthedocs.io/}.
        \item[2023--24] \tab{}Managing Editor and Software Engineer, Australian COVID-19 Modelling Initiative (AUSCMI)
        \item[2022] \tab{}CovStrain, a web-based tool to track global genomic sequencing data on SARS-CoV-2 mutations of interest. 1k users.\ \url{https://covstrain.vercel.app/}.
        \item[2020] \tab{}COVIDVictoria, a web-based tool for COVID-19 Spatial Data Mapping. 2m users.
    \end{tablist}

    \subsection*{Service to the University}
    \begin{tablist}
        \item[2026--] \tab{}Secretary, Faculty of Business and Economics PhD Student Society, University of Melbourne
    \end{tablist}

    \section*{Skills}

    \begin{itemize}
        \item Programming: Python, R, Julia, React, JavaScript, Git, high-performance computing
        \item Languages: English (native), Urdu (fluent)
    \end{itemize}

    % display today's date as Month Year after a vertical space below the end of the text
    \begin{center}
        \vfill
        Updated \monthyeardate\today
    \end{center}
\end{document}
